R Notebook

### 2022-04-28 Code/Simulation.Rmd
code for section 3 (only dependence) plus refactoring

```{r}
# Load packages
library(dgof)
library(tidyverse)
library(copula)
library(evd)
library(ismev)
source('tspb.R')
```

```{r hist_parametric}
# Test parametric bootstrap as a solution to fitting parameters
test_parametric <- function(x, B = 1000) {

# Generate results
n_tests = 100
n = 100
counter <- 0
pvals_parametric <- replicate(n_tests, test_parametric(rnorm(n), B = 1000)$p.value)
counter <- 0
pvals_babu <- replicate(n_tests, test_babu(rnorm(n), B = 1000)$p.value)
pvals_naive <- replicate(n_tests, test_naive(rnorm(n))$p.value)

# Save the histogram figure
ggsave(filename = "hist_fitted.pdf", plot = hist_fitted, path = "../Manuscript", height = 2.1, width = 6)
```

@@

@@

```{r}
test_copula <- function(x, dist, B) {

@@

# Super naive KS-test with fitted parameters
test_super_naive <- function(x) {
  p.value <- ks.test(x, "pnorm", mean = mean(x), sd = sd(x))$p.value
  list(p.value = p.value)
}

@@

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1000
B <- 100

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
counter <- 0

@@

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)

@@

# Generate histograms plot
hist_copula <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("AR = %s", ar))
hist_copula

@@

# Save the histogram figure
ggsave(filename = "hist_copula.pdf", plot = hist_copula, path = "../Manuscript", height = 2.1, width = 6)
```

```{r}
## Test AR(2) model
ptm <- proc.time()

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                            "pnorm", 
                                            B = B))
counter <- 0

@@

# Generate histograms plot
hist_copula_ar2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("AR = (%s, %s)", b1, b2))

@@

hist_copula_ar2

# Save the histogram figure
ggsave(filename = "hist_copula_ar2.pdf", plot = hist_copula_ar2, path = "../Manuscript", height = 2.1, width = 6)
```

```{r}
## Test MA(1) model
ptm <- proc.time()

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), "pnorm", B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)

# Generate histograms plot
hist_copula_ma1 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("MA = %s", ma))

hist_copula_ma1

# Save the histogram figure
ggsave(filename = "hist_copula_ma1.pdf", plot = hist_copula_ma1, path = "../Manuscript", height = 2.1, width = 6)
```

```{r}
## Test ARMA(1,1) model
ptm <- proc.time()

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n),
                                            "pnorm", B = B))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar, 
                                                              ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n))$p.value)

# Generate histograms plot
hist_copula_arma <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("AR = %s, MA = %s", ar, ma))

hist_copula_arma

# Save the histogram figure
ggsave(filename = "hist_copula_arma.pdf", plot = hist_copula_arma, path = "../Manuscript", height = 2.1, width = 6)
```

```{r}
## wcopula: working copula assumed in constructing bootstrap sample
test_copula2 <- function(x, dist, B = 100, wcopula = normalCopula) {
    ## example assuming normal distribution; normal copula
    ## get observed stat
    n <- length(x)
    ## get fitted parameters; could check MASS::fitdistr for general solution
    ## the next two lines only work when dist is normal
    mu <- mean(x)
    sigma <- sd(x)
    stat  <- ks.test(x, dist, mean = mu, sd = sigma)$statistic
    ## get lag-1 sample auto-spearman rho
    rho  <-  cor(x[-1], x[-n], method = "spearman")
    r <- iRho(wcopula(), rho)
    wcop <- wcopula(r)
    ## parametric bootstrap to get an empirical distribution of stat
    stat.b <- double(n)
    ## set up containers
    for (i in 1:B) {
        ## get one bootstrap sample
        ## 1. the marginal distribution is the fitted dist
        ## 2. there is temporal dependence
        u <- runif(n)
        for (j in 2:n) {
            ## could test other copulas later
            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
        }
        ## get bootstrap sample
        ## get fitted parameters for the bootstrap sample
        ## the next lines only work when dist is normal
        x.b <- qnorm(u, mean = mu, sd = sigma)
        mu.b <- mean(x.b)
        sigma.b <- sd(x.b)
        stat.b[i] <- ks.test(x.b, dist, mean = mu.b, sd = sigma.b)$statistic
    }
    ## return empirical p-value    
    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)

## generating observations from a specified distribution with serial dependence
genData <- function(n, qdist, ..., copula, rho) {
    ## n: sample size
    ## qdist: quantile function of the desired marginal distribution
    ## copula: copula for serial distribution
    ## rho: spearman's rho
    theta <- iRho(copula(), rho)
    cop <- copula(theta)
    u <- runif(n)
    for (j in 2:n) {
        u[j] <- cCopula(c(u[j-1], u[j]), cop, indices = 2, inverse = TRUE)
    }
    qdist(u, ...)
}

# Naive KS-test
test_naive_copula <- function(x) {
  p.value <- ks.test(x, "pnorm")$p.value
  list(p.value = p.value)
}

# Generate results
n <- 100
rho <- 0.5
counter <- 0
nrep <- 100
B <- 100
pvals_copula <- replicate(nrep, test_copula2(genData(n, qnorm, mean = 1, sd = 1, copula = claytonCopula, rho = rho), "pnorm", B = B))
pvals_naive <- replicate(nrep, test_naive_copula(genData(n, qnorm, mean = 1, sd = 1, copula = claytonCopula, rho = rho))$p.value)

# Generate histograms plot
hist_copula2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

hist_copula2

# Save the histogram figure
#ggsave(filename = "hist_copula_c2.pdf", plot = hist_copula_c, path = "../Manuscript", height = 2.1, width = 6)
```

```{r}
# Testing bootstrap with copulas for gamma distribution
test_gamma <- function(x, dist, B = 100, wcopula = normalCopula) {

@@

# Set variables
n <- 100
rho <- 0.7
counter <- 0
nrep <- 1000
B <- 1000
shape <- 3
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gamma(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho), "pgamma", B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric_gamma(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho))$p.value)

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho))$p.value)

@@

# Generate histograms plot
hist_copula_gamma <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("Rho = %s, Shape = %s, Scale = %s", rho, shape, scale))

@@

hist_copula_gamma

# Save the histogram figure
ggsave(filename = "hist_copula_gamma.pdf", plot = hist_copula_gamma, path = "../Manuscript", height = 2.1, width = 6)
```

```{r}
# Testing bootstrap with copulas for GEV distribution
test_gev <- function(x, B = 100, wcopula = normalCopula) {

@@

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 100
loc <- 0
shape <- 0.2
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gev(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho), B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- suppressWarnings(replicate(nrep, test_parametric_gamma(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho))$p.value))

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho))$p.value)

@@

# Generate histograms plot
hist_copula_gev <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("Rho = %s, Loc = %s, Shape = %s, Scale = %s", rho, loc, shape, scale))

@@

hist_copula_gev

# Save the histogram figure
ggsave(filename = "hist_copula_gev.pdf", plot = hist_copula_gev, path = "../Manuscript", height = 2.1, width = 6)
```

```{r}
ptm <- proc.time()

# Super naive KS-test with fitted parameters
test_super_duper_naive <- function(x) {
  p.value <- ks.test(x, "pnorm", mean = 0, sd = 1)$p.value
  list(p.value = p.value)
}

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1000
B <- 100

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_duper_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)

# Generate histograms plot
hist_copula_only <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("AR = %s", ar))
hist_copula_only

# Save the histogram figure
ggsave(filename = "hist_copula_only.pdf", plot = hist_copula_only, path = "../Manuscript", height = 2.1, width = 6)
```

>>>>

```{r}
# Load packages
library(tidyverse)
library(copula)
library(evd)
library(ismev)
source('tspb.R')
```

@@

```{r Parametric}
# Test parametric bootstrap as a solution to fitting parameters
test_parametric <- function(x, B = 1000) {

# Generate results
n_tests = 1000
n = 100
counter <- 0
pvals_parametric <- replicate(n_tests, test_parametric(rnorm(n), B = 1000)$p.value)
counter <- 0
pvals_babu <- replicate(n_tests, test_babu(rnorm(n), B = 1000)$p.value)
pvals_naive <- replicate(n_tests, test_naive(rnorm(n))$p.value)

# Save the histogram figure
ggsave(filename = "hist_fitted.pdf", plot = hist_fitted, path = "../Manuscript", height = 2.1, width = 6)

data_new <- results                              # Replicate data
data_new$histogram <- factor(data_new$histogram,      # Reordering group factor levels
                         levels = c("Naive", "Parametric", "Babu"))

# Generate histograms plot
hist_fitted <- ggplot(data_new) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_fitted
```

@@

```{r gen_data}
## generating observations from a specified distribution with serial dependence
genData <- function(n, qdist, ..., copula, rho) {
    ## n: sample size
    ## qdist: quantile function of the desired marginal distribution
    ## copula: copula for serial distribution
    ## rho: spearman's rho
    theta <- iRho(copula(), rho)
    cop <- copula(theta)
    u <- runif(n)
    for (j in 2:n) {
        u[j] <- cCopula(c(u[j-1], u[j]), cop, indices = 2, inverse = TRUE)
    }
    qdist(u, ...)
}
```

```{r AR(1) D}
test_copula_D <- function(x, dist, B, mean, sd) {

    # Get observed statistic
    n <- length(x)

    stat  <- ks.test(x, dist, mean = mean, sd = sd)$statistic

        # Transform bootstrap sample and fit the parameters
        x.b <- qnorm(u, mean = mean, sd = sd)

        # Gather bootstrap sample's test statistic
        stat.b[i] <- ks.test(x.b, dist, mean = mean, sd = sd)$statistic
    }

# Standard KS test
test_standard_ks <- function(x, mean, sd) {
  p.value <- ks.test(x, "pnorm", mean = mean, sd = sd)$p.value
  list(p.value = p.value)
}

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 500
B <- 100
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                              "pnorm", 
                                              B = B, 
                                              mean = mean, 
                                              sd = sd))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                                mean = mean, 
                                                sd = sd)$p.value)

# Generate histograms plot
hist_ar1_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar1_D

# Save the histogram figure
ggsave(filename = "hist_ar1_D.pdf", plot = hist_ar1_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r MA(1) D}
ptm <- proc.time()

# Set variables
n <- 100
counter <- 0
nrep <- 100
B <- 100
ma <- 0.5
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                              "pnorm", 
                                              B = B,
                                              mean = mean,
                                              sd = sd))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n),
                                                mean = mean,
                                                sd = sd)$p.value)

# Generate histograms plot
hist_ma1_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ma1_D

# Save the histogram figure
ggsave(filename = "hist_ma1_D.pdf", plot = hist_ma1_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r ARMA(1,1) D}
ptm <- proc.time()

# Set variables
n <- 100
counter <- 0
nrep <- 100
B <- 100
ar <- 0.5
ma <- 0.3
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                            "pnorm", 
                                            B = B,
                                            mean = mean,
                                            sd = sd))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n))$p.value)

# Generate histograms plot
hist_arma_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_arma_D

# Save the histogram figure
ggsave(filename = "hist_arma_D.pdf", plot = hist_arma_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r AR(2) D}
ptm <- proc.time()

# Set variables
n <- 100
counter <- 0
nrep <- 100
B <- 100
b1 <- 0.5
b2 <- 0.3
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                            "pnorm", 
                                            B = B,
                                            mean = mean,
                                            sd = sd))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n),
                                                mean = mean,
                                                sd = sd)$p.value)

# Generate histograms plot
hist_ar2_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar2_D

# Save the histogram figure
ggsave(filename = "hist_ar2_D.pdf", plot = hist_ar2_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r Gamma D}
# Testing bootstrap with copulas for gamma distribution
test_gamma_D <- function(x, dist, B = 100, wcopula = normalCopula, shape, scale) {

    # Get observed stat
    n <- length(x)

        # Calculate new test statistic
        stat.b[i] <- ks.test(x.b, dist, shape = shape, scale = scale)$statistic
    }

# Naive function that incorrectly uses fitted parameters for gamma distribution
test_standard_gamma <- function(x, shape, scale) {
  p.value <- ks.test(x, "pgamma", shape = shape, scale = scale)$p.value
  list(p.value = p.value)
}

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 100
B <- 100
shape <- 3
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gamma_D(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                             "pgamma", 
                                             B = B,
                                             shape = shape,
                                             scale = scale))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_gamma(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                   shape = shape, 
                                                   scale = scale)$p.value)

# Generate histograms plot
hist_gamma_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_gamma_D

# Save the histogram figure
ggsave(filename = "hist_gamma_D.pdf", plot = hist_gamma_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r GEV D}
# Testing bootstrap with copulas for GEV distribution
test_gev_D <- function(x, B = 100, wcopula = normalCopula, loc, scale, shape) {

    # Get observed stat
    stat  <- ks.test(x, 'pgev', loc = loc, scale = scale, shape = shape)$statistic

        # Transform the bootstrap sample
        x.b <- qgev(u, loc = loc, scale = scale, shape = shape)

        # Calculate bootstrap test statistic
        stat.b[i] <- ks.test(x.b, 'pgev', loc = loc, scale = scale, shape = shape)$statistic
    }

# Standard KS test for GEV distribution
test_standard_gev <- function(x, loc, scale, shape) {
  p.value <- ks.test(x, "pgev", loc = loc, scale = scale, shape = shape)$p.value
  list(p.value = p.value)
}

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 100
B <- 100
loc <- 0
shape <- 0.2
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gev_D(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
                                           loc = loc, 
                                           shape = shape,
                                           scale = scale,
                                           B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_gev(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                 loc = loc, 
                                                 shape = shape,
                                                 scale = scale)$p.value)

# Generate histograms plot
hist_gev_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_gev_D

# Save the histogram figure
ggsave(filename = "hist_gev_D.pdf", plot = hist_gev_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r Copula FD}
test_copula_D <- function(x, dist, B) {

@@

# Super naive KS-test with fitted parameters
test_standard_ks_F <- function(x) {
  p.value <- ks.test(x, "pnorm", mean = mean(x), sd = sd(x))$p.value
  list(p.value = p.value)
}

@@

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1000
B <- 1000

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
counter <- 0

@@

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks_F(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
results <- data_frame(p_values, histogram)
save(results, file = "results_copula.RData")

# Generate histograms plot
hist_ar1_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar1_D

# Save the histogram figure
ggsave(filename = "hist_ar1_D", plot = hist_ar1_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r MA(1) FD}
## Test MA(1) model
ptm <- proc.time()

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), "pnorm", B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks_F(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)

@@

# Generate histograms plot
hist_ma1_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_ma1_D

# Save the histogram figure
ggsave(filename = "hist_ma1_D.pdf", plot = hist_ma1_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r ARMA(1,1) FD}
## Test ARMA(1,1) model
ptm <- proc.time()

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n),
                                            "pnorm", B = B))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks_F(arima.sim(list(ar = ar, 
                                                              ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n))$p.value)

# Generate histograms plot
hist_arma_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

hist_arma_D

# Save the histogram figure
ggsave(filename = "hist_arma_D.pdf", plot = hist_arma_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r AR(2) FD}
## Test AR(2) model
ptm <- proc.time()

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                            "pnorm", 
                                            B = B))
counter <- 0

@@

# Generate histograms plot
hist_ar2_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_ar2_D

# Save the histogram figure
ggsave(filename = "hist_ar2_D.pdf", plot = hist_ar2_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r Gamma FD}
# Testing bootstrap with copulas for gamma distribution
test_gamma_FD <- function(x, dist, B = 100, wcopula = normalCopula) {

@@

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
shape <- 3
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gamma_FD(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), "pgamma", B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric_gamma(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value)

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value)

@@

# Generate histograms plot
hist_gamma_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_gamma_FD

# Save the histogram figure
ggsave(filename = "hist_gamma_FD.pdf", plot = hist_gamma_FD, path = "../Manuscript", height = 2.1, width = 6)
```

```{r GEV FD}
# Testing bootstrap with copulas for GEV distribution
test_gev_FD <- function(x, B = 100, wcopula = normalCopula) {

@@

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
loc <- 0
shape <- 0.2
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gev_FD(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- suppressWarnings(replicate(nrep, test_parametric_gamma(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value))

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value)

@@

# Generate histograms plot
hist_gev_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_gev_FD

# Save the histogram figure
ggsave(filename = "hist_gev_FD.pdf", plot = hist_gev_FD, path = "../Manuscript", height = 2.1, width = 6)
```
